Learned image compression

### 2023-03-20 paper/paper.tex
update

\begin{figure*}[h!]
    \centering
    \includegraphics[width=7in]{architecture.png}
    \caption{Architecture of full ELIC \cite{ELIC}. The
blue and red arrows denote the encoding and decoding data flow. The orange ones are shared by both encoding and decoding. MAKE THE FIGURE AND CAPTION TO SPAN 2 COLUMNS}
    \label{fig:architecture}
\end{figure*}

@@

@@

% \begin{minipage}
% \begin{flushleft}
% \end{flushleft}
% \begin{itemize}
%     \item[] Row (Model) 1: epoch=250 | $\lambda$=8e-4 | N=M=192, 
%     \item[] Row (Model) 2: epoch=300 | $\lambda$=4e-4 | N=128, M=192, 
%       \item[] Row (Model) 3: epoch=300 | $\lambda$=8e-4 | N=128, M=192, 
%       \item[] \textbf{Row (Model) 4}: epoch=300 | $\lambda$=1e-2 | N=M=192
% \end{itemize}
% \end{flushleft}
% \end{minipage}

\begin{figure}[h!]
\begin{minipage}[b]{0.8\linewidth}
    \centering
    \includegraphics[width=7.5cm]{psnr_mssim.png}
\end{minipage}
\begin{minipage}[b]{0.8\linewidth}

    \centering
    \includegraphics[width=7.5cm]{per_img.png}
\end{minipage}
    \label{fig:architecture}
    \caption{Architecture of full ELIC \cite{ELIC}. The
blue and red arrows denote the encoding and decoding data flow. The orange ones are shared by both encoding and decoding. MAKE THE FIGURE AND CAPTION TO SPAN 2 COLUMNS}
\end{figure}

\begin{figure*}[h!]
\centering
\begin{minipage}[b]{.8\linewidth}
    \centering
    \includegraphics[width=\linewidth]{reconstruction.png}

\end{minipage}
\begin{minipage}[b]{.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{comparison.png}
\end{minipage}
    \caption{Architecture of full ELIC \cite{ELIC}. The
blue and red arrows denote the encoding and decoding data flow. The orange ones are shared by both encoding and decoding. MAKE THE FIGURE AND CAPTION TO SPAN 2 COLUMNS}
    \label{fig:architecture}
\end{figure*}

>>>>

\begin{figure*}[h!]
    \centering
    \includegraphics[width=7in]{architecture.png}
    \caption{Architecture of full ELIC \cite{ELIC}. The
blue and red arrows denote the encoding and decoding data flow. The orange ones are shared by both encoding and decoding.}
    \label{fig:architecture}
\end{figure*}

@@

\begin{table}[!h]
\label{table:models}
\begin{center}
\begin{tabular}{c c c}
    Row (Model) 1: epoch=250 & $\lambda$=8e-4 & N=M=192 \\
    Row (Model) 2: epoch=300 & $\lambda$=4e-4 & N=128, M=192 \\
    Row (Model) 3: epoch=300 & $\lambda$=8e-4 & N=128, M=192 \\
    \textbf{Row (Model) 4}: epoch=300 & $\lambda$=1e-2 & N=M=192 \\
\end{tabular}
\end{center}
\end{table}

\vfill

\begin{figure}[h!]
\begin{minipage}[b]{0.8\linewidth}
    \centering
    \includegraphics[width=7.2cm]{kodak_fixed.png}
    \centerline{(a) Average values over KODAK dataset \cite{kodak}.}\medskip
\end{minipage}
\begin{minipage}[b]{0.8\linewidth}

    \centering
    \includegraphics[width=7.2cm]{kodak_per_fixed.png}
    \centerline{(b) Performance on individual images of KODAK dataset \cite{kodak}.}\medskip
\end{minipage}
    \label{fig:results}
    \caption{Results on KODAK dataset \cite{kodak}.}
\end{figure}

@@

\begin{figure*}[h!]
\centering
\begin{minipage}[b]{.8\linewidth}
    \centering
    \includegraphics[width=\linewidth]{reconstruction.png}
    \centerline{(a)  Result images from our models. Each row is results from the model 1 to 4 respectively}\medskip

\end{minipage}
\begin{minipage}[b]{.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{comparison.png}
    \centerline{(b) Comparisons to conventional image compression methods JPEG and BPG to our results from Model 3 and original image.}\medskip
\end{minipage}
    \caption{Result/comparison images.}
    \label{fig:images}
\end{figure*}
